Dissecting Neural Style Transfer

### 2019-06-04 paper/paper.tex

\section{Conclusion and Future Work}

>>>>

\section{Conclusion}
We have successfully implemented neural style transfer and generated the blende pastiche image
using content image and style image. We have finally concluded that Artistic image is created
with the help of pre-trained CNN. we did use vgg-19 model which is pre-trained model for object 
and face detection and we saw how effectively it was able to detect the texture,and contour of
the image. We determine the content loss by selecting a particular hidden layer’s activation. 
We also determined the style loss with help of Gram Matrix of the hidden layer’s activations.
Total style loss was computed by summing up all the style loss till the layers from where the
content image is selected. Losses were evaluated by using gradient loss dynamically. This was
computed using optimization algorithm of Broyden–Fletcher–Goldfarb–Shanno. This was done by 
inputting the every iteration loss to the network.

\section{Observation}
We found out that we can modify how much style of style image can be inserted in the final image. 
In order to do this, we determined how much content and style of the content image and style image
need to be present. These can be used as hyper parameters to develop the final artistic image. 
More weights of the style of the style image leads to more style and content of the style image
are going to be present in the generated image vice-versa. Another hyper parameter is to choose
the CNN hidden layer activation for the content image. This helps to decide how much content
of content images needs to present in the generated image.

\section{Discussion}
We did find that by putting more weights to style image, more style and content of style images
were getting displayed. By putting in the context, when weights are 105  then content and style
of the content image is lost and style of style image is on the generated image but content of
style image was distorted. In the another process, we did choose different hidden activation layer
in CNN for content image. Ideally, we have selected the middle layer which is ‘CONV_4’. We can
select any of convolution layer to see different result. We found out that by selecting the CONV_1,
the textures of the content image are more prominent. We also found it amazing that after the certain
number of iterations, we are getting blacked out image. It could be possible that losses would have
become zero in this case which further altering the pixel values of the image. However, this is 
something need to be researched Thoroughly.

\section{Lessons Learnt}
We were able to use Pytorch and Tensorflow libraries to implement the image stylization.
We also understood how well CNN model works when image is given as input. We learned to 
compute difference between the two images with the help of content and style. This can be 
computed with the help of gradient loss.

\section {Future Work}
At present, we are applying style of the style image to the whole content image. We are thinking
of using image segmentation technique[1] so to apply style on a particular segment of the image. 
For example, there is a photograph of person wearing a jacket, applying this new technique, 
we would style the jacket with help of some art and apply it back to original image. This means 
old jacket becomes the new one.

\section{Summary of Learning Outcome} 
We learned some crucial concept of programming the project in python using pyTorch and Tensorflow. 
We analysed and evaluated neural style transfer algorithm. We also learned to examined the research
paper and how to link the research paper with other researches to form an innovation solutions. 
We also learned to work in a team. We were able to reflect and use the course learning as our future
work for the neural style transfer.
